\documentclass{res}

\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}

\begin{document}
    \name{Inessa Vasilevskaya}
    \begin{resume}
        \section{Contacts:}
        {\bf email:} inavasilevskaya@gmail.com \\
        {\bf mobile:} +7 903 5812385\\
        {\bf github:} https://github.com/fernflower\\
        \section{Skills:}
        \begin{itemize}
            \item Mainly used Python for production in the last 3 years due to openstack related activity. Will have no problem writing clean, extendable and testable code in
                Java, C\#, C++ given some time to adapt. Would love to try Golang in production.

            \item Have knowledge in algorithms, data structures, computer architecture, operating systems design, networking, relational databases.

            \item Advanced Linux user and administrator

            \item Good team player

            \item Believe that flexible hours and part-time work availability is crucial for good work-life balance

        \end{itemize}

        \section{Work experience:}
        \begin{itemize}
            \item \textit{Apr 2016~-- now}
                \textbf{Mirantis, part-time software developer}

                Upstream contributions to openstack/neutron project: bug triaging and fixing; Providing support for networking related issues in Mirantis Open Stack product.

                Technological stack: Python 2.7, openstack, Open vSwitch, DPDK, bash, git, gerrit

            \item \textit{Oct 2014~-- Jun 2015}
                \textbf{Mirantis, software developer}

                Upstream contributions to openstack/glance project: bug triaging and fixing, documentation, new features development; Providing support for glance-related issues in Mirantis Open Stack product.

                Technological stack: Python 2.7, openstack, MySQL, bash, git, gerrit
            \item \textit{Feb 2013~-- Aug 2014}
                \textbf{Teleshkola, software developer}

                Participated in development of a web-based distant education system (server side).

                Technological stack: Python 2.7/3.3, PostgreSQL, bash, XML, XSLT, git
            \item \textit{May 2012~-- Feb 2013}
                \textbf{OAO Gasprombank, part-time software developer}

                Development and support of an automated rss-feed based monitoring system

                Technological stack: Java, MongoDB, git

            \item \textit{Nov 2011~-- Apr 2012}
                \textbf{Analytical centre under the government of Russian Federation, part-time software developer}

                Nagios monitoring system administration and custom plugins development; Development and support of an automated rss-feed based monitoring system

                Technological stack: Java, MongoDB, git, Nagios

        \end{itemize}

        \section{Education:}
        \begin{itemize}
          \item \textit{2011~--2013}

              Moscow State University, Master's degree in Applied Mathematics and Computer Science (cum laude)

            \item \textit{2007~---2011}

              Moscow State University, Bachelor's degree in Applied Mathematics and Computer Science (cum laude)

            \item \textit{2005~--2007}

             School 41, Minsk
        \end{itemize}

    \section{Languages:}
        \begin{itemize}
            \item English~-- advanced
            \item Russian~-- native speaker
            \item German~-- can order a beer
        \end{itemize}


    \section{Hobbies:} urban orienteering, double bass, diy projects with raspberry pi.
\end{resume}
\end{document}
